Report

### 2021-12-15 report.Rmd
Update report.Rmd

Tables 3 and 4 show the main results from our replication.  Without adjusting for distances to providers, we found that highly restrictive legislation was associated with a  reduction in abortions of 0.922 per 1,000 women, and that effect was reduced to 0.828 when adjusting for distances to providers.  These effects were roughly twice as large as the effects calculated by Brown et al., nevertheless our estimates were within their reported 95% confidence intervals (see Brown et al. Table 3).

>>>>

Tables 3 and 4 show the main results from our replication.  Without adjusting for distances to providers, we found that highly restrictive legislation was associated with a  reduction in abortions of 0.814 per 1,000 women, and that effect was reduced to 0.649 when adjusting for distances to providers.  These effects were roughly twice as large as the effects calculated by Brown et al., nevertheless our estimates were within their reported 95% confidence intervals (see Brown et al. Table 3).
